\Title

### 2015-11-02 manuscript.tex
Draft of regularized bott section

\begin{equation}
    \mathbf{A} = 2\pi G \Delta \rho \mathbf{I},
    \label{eq:bott-jacobian}
\end{equation}

@@

Approximate the Jacobian by making tesseroid size tend to infinity to get
Bouguer slab.
This approximation is good for tesseroids because each will cover a large
enough area.
Show case for the Steepest Descent.
Extend the Jacobian to include lateral density variation.
Important because density-contrast is positive or negative depending if the
Moho is above or below the reference level.
Enforce that the use of a particular

Biggest computation time is in forward modeling.
All matrices involved are sparse.
Solve the sparse linear system with a conjugate gradient method.
\todo{Check which conjugate gradient scipy.space.linalg.solve uses.}
Use the regularized inversion because multiplying and solving the linear system
are fast compared to forward modeling.
Not using step size optimization because forward modeling is very slow so
increased convergence doesn't justify the extra time spent on the discarded
step attempts.

@@

\todo{Cite packages in the references.txt file.}

>>>>

\begin{equation}
    \mathbf{A} = 2\pi G \Delta \rho \mathbf{I},
    \label{eq:bott-gaussnewton}
\end{equation}

@@

We propose a regularized version of Bott's method to invert for the relief of
the anomalous Moho in spherical coordinates.
Our formulation maintains the regularized solutions
for Gauss-Newton (Eq.~\ref{eq:gaussnewton-regul}) and
Steepest Descent (Eq.~\ref{eq:steepest-regul})
but replaces the full Jacobian matrix with the Bouguer plate approximations
(respectively, Eq.~\ref{eq:bott-gaussnewton} and \ref{eq:bott-steepest}).
This linearizes the Jacobian matrix and reduces it to a sparse diagonal matrix,
thus eliminating the cost of computing and storing $\mathbf{A}$.
Matrix arithmetic operations can be performed efficiently by taking advantage
of the sparse nature of matrices $\mathbf{A}$ and $\mathbf{R}$.
The same is true for solving the equation system in the Gauss-Newton method
(Eq.~\ref{eq:gaussnewton-regul}).
However, the computational cost of forward modeling is still present.
Particularly, forward modeling using tesseroids is more computationally
intensive than using right-rectangular prisms
because of the numerical integration and adaptive discretization.
Benchmarks suggest that forward modeling accounts for approximately $99\%$ of
\todo{Checar esse número}
the computation time for a Gauss-Newton inversion
(see supplementary material)\todo{Referência melhor pra isso}.
Hence, this formulation allows us to retain the efficiency of Bott's method
while stabilizing the solution through the well established formalism of
Tikhonov regularization.

@@

\todo{Cite packages in the references.txt file.}
\todo{Check which conjugate gradient scipy.space.linalg.solve uses.}
